AIR4children: Artificial Intelligence and Robotics for Children

### 2021-02-09 article/tex/submission.tex
adds DonatoBadilloPerez contribution to the conclusions

\section{Conclusions and future work}
[for conclusions and future work].
The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.
A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

>>>>

\section{Conclusions and future work}
In our fast-evolving world towards technology is important to teach children what
they are going to face when they grow up, unfortunately many children don’t have
access to technology or the opportunity to learn about robotics and AI, and others,
although they already know this type of technology, they don’t know how it works
and how to create more of this technology which is really important towards the
future. This project aims for that goal, create a free space where we can help
children know and comprehend the functionality of Robotics and AI so they can
obtain the best of it and create even more technology, with a positive impact in
society, regardless of their opportunities or status, we believe that every children
has the potential to learn and create.
